Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-05-03 analysis/paper/paper.Rmd
Add a bit more about evaluting the models

Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn in. The remaining 50,000 samples were thinned by taking every tenth sample resulting in 5,000 independent draws from the posterior distribution of the parameters of the model. The `coda` [@coda2006] package was used to provide utilities to check convergence using visual inspection of graphs and the Gelman-Rubin test. All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].

@@

>>>>

Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn in. The remaining 50,000 samples were thinned by taking every tenth sample resulting in 5,000 independent draws from the posterior distribution of the parameters of the model. The `coda` [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman-Rubin test. All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].

@@

### The Interaction of Irrigation and N Management
